<!-- Report template, please replace {TOOL}  -->

```{r,echo=FALSE}
# Only change this variables
input_file <- "#RESULTSENV#"
sample_name <- "#NAMEENV#"

abricate_input <- read.csv(file = input_file, header = TRUE, sep = '\t', check.names=FALSE)

# calling libs
suppressMessages(library(plotly))
suppressMessages(library(ggplot2))
suppressMessages(library(htmlwidgets))
suppressMessages(library(dplyr))
suppressMessages(library(DT))
```

### Report templates

#### Description

This sample contains `r nrow(abricate_input)`" resistance genes.
Which Database is used .. ncbi


#### Results
<!-- simple table, #RESULTSENV# will be replaced via nextflow process -->
```{r,echo=FALSE}
# Produce Table
selected_input <- abricate_input %>% select(SEQUENCE, START, END, STRAND, GENE, ACCESSION, PRODUCT, RESISTANCE)
datatable(selected_input, extensions = 'Buttons', options = list(
  searching = TRUE,
  pageLength = 10,
  lengthMenu = c(5, 10, 15, 20),
  buttons = c('copy', 'csv', 'excel', 'colvis')
))
```

```{r,echo=FALSE,fig.width = 9, fig.height = 9}



# remove duplicates
df <- abricate_input %>% select(GENE, RESISTANCE)
df_mod <- df [!duplicated(df),]

# parcing columns into lists
gene <- c(df_mod$GENE)
resistance <- c(df_mod$RESISTANCE)
sample <- c(sample_name)
empty <- c('')

# count list elements
gene_count = length (gene)
resistance_count = length (resistance)

# list for Sample_Name
sample_list<- rep(sample, resistance_count)

# append lists
label_list <- append(sample, resistance)
parent_list <- append(empty, sample_list)

# append list
labels_final <- append(label_list, gene)
parents_final <- append(parent_list, resistance)

#plotting
plot_ly(
  labels = labels_final,
  parents = parents_final,
  type = 'sunburst'
)

```
**Figure.1**: Interactive sunburst chart showing the detected resistances in the sample. The first ring shows the resistances and the second the associated resistance genes. Plot can be saved in the right upper corner.


#### Citation
If you publish the results use following citation:

Seemann T, Abricate, Github https://github.com/tseemann/abricate
NCBI AMRFinderPlus - doi: 10.1128/AAC.00483-19
