<!-- Report template, please replace {TOOL}  -->
### ABRicate
 
```{r,echo=FALSE}
# calling libs
suppressMessages(library(plotly))
suppressMessages(library(ggplot2))
suppressMessages(library(htmlwidgets))
suppressMessages(library(dplyr))
suppressMessages(library(DT))

# Only change this variables
SAMPLE_NAME <- "#NAMEENV#"
INPUT_FILE <- "#RESULTSENV#"
VERSION <- "#TOOLVERSIONENV#"
DB_VERSION <- "#DBVERSIONENV#"
COMMAND <- "#COMMANDENV#"
OUTPUT_PATH <- "#PATHENV#"

ABRICATE_INPUT <- read.csv(file = INPUT_FILE, header = TRUE, sep = '\t', check.names=FALSE)
DATABASE_NAME <- ABRICATE_INPUT %>% select (DATABASE)
ABRICATE_SAMPLE <- nrow(ABRICATE_INPUT)
ABRICATE_DATABASE <- DATABASE_NAME [!duplicated(DATABASE_NAME),]
```
ABRicate is a tool for mass screening of contigs for antimicrobial resistance or virulence genes.  

#### Data

Sample name: **`r SAMPLE_NAME`**  

ABRicate version used: **`r VERSION`**  

Database version(s): **`r DB_VERSION`**

Command used: **`r COMMAND`**

Results are stored in: **`r OUTPUT_PATH`**  

#### Overview
`r if(nrow(ABRICATE_INPUT)>0) { 
  sprintf("The sample **%s** contains **%s** resistance genes. Determined by ABRicate using the **%s** Database.",
                    SAMPLE_NAME, ABRICATE_SAMPLE, ABRICATE_DATABASE)
} else { 
  sprintf("**No resistance genes have been found in your sample!**")
}`

```{r,echo=FALSE,fig.width = 9, fig.height = 9}

if (nrow(ABRICATE_INPUT)>0){
# remove duplicates
DF <- ABRICATE_INPUT %>% select(GENE, RESISTANCE)
DF_MOD <- DF [!duplicated(DF),]

# parcing columns into lists
GENE <- c(DF_MOD$GENE)
RESISTANCE <- c(DF_MOD$RESISTANCE)
RESISTANCE_UNIQUE <- RESISTANCE[!duplicated(RESISTANCE)]
SAMPLE <- c(SAMPLE_NAME)
EMPTY <- c('')

# count list elements
GENE_COUNT = length (GENE)
RESISTANCE_COUNT = length (RESISTANCE_UNIQUE)

# list for Sample_Name
SAMPLE_NAME_UNIQUE <- rep(SAMPLE, RESISTANCE_COUNT)

# append lists
LABEL_LIST <- append(SAMPLE, RESISTANCE_UNIQUE)
PARENT_LIST <- append(EMPTY, SAMPLE_NAME_UNIQUE)

LABELS_FINAL <- append(LABEL_LIST, GENE)
PARENTS_FINAL <- append(PARENT_LIST, RESISTANCE)

#plotting
plot_ly(
  labels = LABELS_FINAL,
  parents = PARENTS_FINAL,
  type = 'sunburst'
)
}
```
`r if(nrow(ABRICATE_INPUT)>0){ 
  sprintf("**Fig.1**: Interactive sunburst chart showing the detected resistances in **%s**. The first ring shows the resistances and the second the associated resistance genes.
For filtering the results after resistances click on it. The plot can be saved in the right upper corner.",
SAMPLE_NAME)
}`

`r if(nrow(ABRICATE_INPUT)>0){ 
  sprintf("#### Resistance gene table\n
  **Tab.1**: Interactive table showing the abricate raw data for the sample **%s**. You can filter and download the table directly.", 
  SAMPLE_NAME)
}`

```{r,echo=FALSE}
# Produce Table
if (nrow(ABRICATE_INPUT)>0){
SELECTED_INPUT <- ABRICATE_INPUT %>% select(SEQUENCE, START, END, STRAND, GENE, ACCESSION, PRODUCT, RESISTANCE)

DTABLE <- datatable(SELECTED_INPUT, 
  rownames = FALSE, 
  class = 'hover', 
  extensions  = 'Buttons', 
  filter = list(position = 'top'),
  options = list(
    search = list(regex = TRUE, caseInsensitive = FALSE),
    pageLength = 10,
    lengthMenu = c(5, 10, 15, 20),
    dom = '<"top"fB>rt<"bottom"lp>i<"clear">', 
    buttons = c('copy', 'csv', 'excel', 'pdf', 'colvis')
  )
)
DTABLE 
}
```

#### Links and Citation
If you publish the results use following citation:

Seemann T, Abricate, Github https://github.com/tseemann/abricate  
NCBI AMRFinderPlus - doi: 10.1128/AAC.00483-19  
CARD - doi:10.1093/nar/gkw1004  
Resfinder - doi:10.1093/jac/dks261  
PlasmidFinder - doi:10.1128/AAC.02412-14  
