<!-- Report template, please replace {TOOL}  -->

### Busco
 
```{r,echo=FALSE}
# Only change this variables
input_file <- "#RESULTSENV#"
sample_name <- "#NAMEENV#"
busco_database <- "#DBVERSIONENV#"

# calling libs
suppressMessages(library(plotly))
suppressMessages(library(ggplot2))
suppressMessages(library(htmlwidgets))
suppressMessages(library(dplyr))
suppressMessages(library(DT))

busco_input <- read.csv(file = input_file, header = TRUE, sep = '\t', check.names=FALSE)
```
Busco is a tool to determine the completeness of a bacterial genome.  

#### Data

Sample name: **#NAMEENV#**  

Busco version used: **#TOOLVERSIONENV#**   

Database versions: **#DBVERSIONENV#**

Command used: **#COMMANDENV#**

Results are stored in: **#PATHENV#**  

#### Overview
`r if(nrow(busco_input)>0) { 
  sprintf("The sample **%s** contains X busco genes. Determined by Busco using the **%s** Database.",
                    sample_name, str_split_i(busco_database, ' ', 0))
} else { 
  sprintf("**The output file is empty; no Busco genes were recorded.**")
}`

```{r,echo=FALSE}
#GRAPHCODEBLOCK#
```

```{r,echo=FALSE}
# Produce Table
if (nrow(busco_input)>0){

DTABLE <- datatable(busco_input, 
  rownames = FALSE, 
  class = 'hover', 
  extensions  = 'Buttons', 
  filter = list(position = 'top'),
  options = list(
    search = list(regex = TRUE, caseInsensitive = FALSE),
    pageLength = 10,
    lengthMenu = c(5, 10, 15, 20),
    dom = '<"top"fB>rt<"bottom"lp>i<"clear">', 
    buttons = c('copy', 'csv', 'excel', 'pdf', 'colvis')
  )
)
DTABLE 
}
```

#### Links and Citation
If you publish the results use following citation:

