<!-- Report template, please replace {TOOL}  -->

### Busco

```{r,echo=FALSE}
# calling libs
suppressMessages(library(plotly))
suppressMessages(library(ggplot2))
suppressMessages(library(grid))
suppressMessages(library(htmlwidgets))
suppressMessages(library(dplyr))
suppressMessages(library(DT))

# Only change this variables
SAMPLE_NAME <- "#NAMEENV#"
INPUT_FILE <- "#RESULTSENV#"
VERSION <- "#TOOLVERSIONENV#"
DB_VERSION <- "#DBVERSIONENV#"
COMMAND <- "#COMMANDENV#"
OUTPUT_PATH <- "#PATHENV#"

BUSCO_INPUT <- read.csv(file = INPUT_FILE, header = TRUE, sep = '\t', check.names=FALSE)
BUSCO_DATABASE_BASE_NAME <- strsplit(DB_VERSION, ' ')[[1]][1]

ALL_GENES_LIST <- #PLOT_ABSOLUTE_VALUES#
COMPLETE_GENES_SINGLE_NR <- ALL_GENES_LIST[1]
COMPLETE_GENES_DUPLICATE_NR <- ALL_GENES_LIST[2]
FRAGMENTED_GENES_NR <- ALL_GENES_LIST[3]
MISSING_GENES_NR <- ALL_GENES_LIST[4]
TOTAL_BUSCO_GENE_COUNT <- Reduce('+', ALL_GENES_LIST)
```
Busco ("Benchmarking Universal Single-Copy Orthologs") is a tool to assess genome completeness for microbial genomes.
It uses a group-specific set of single-copy orthologous genes, defined via the used database.
For the searched genes four states are possible: [C:complete], [D:duplicated], [F:fragmented], [M:missing].
The recovered genes are classified as ‘complete’ when their lengths are within two standard deviations of 
the BUSCO group mean length (i.e. within ∼95% expectation).
"D" hints towards a contamination, while "F" & "M" are indicating a incomplete genome. 

#### Data

Sample name: **`r SAMPLE_NAME`**  

Busco version used: **`r VERSION`**   

Database versions: **`r DB_VERSION`**

Command used: **`r COMMAND`**

Results are stored in: **`r OUTPUT_PATH`**  

#### Overview
`r sprintf("**%s** Busco-genes were searched in sample **%s**:\n**%s** are complete single-copy genes;\n**%s** are complete but duplicated genes;\n**%s** genes are fragmented;\n and **%s** genes are missing.\nDetermined by Busco using the **\"%s\"**-Database.",
                    TOTAL_BUSCO_GENE_COUNT, SAMPLE_NAME, COMPLETE_GENES_SINGLE_NR, COMPLETE_GENES_DUPLICATE_NR, FRAGMENTED_GENES_NR, MISSING_GENES_NR, BUSCO_DATABASE_BASE_NAME)`

```{r,echo=FALSE}
# BUSCO summary figure
# @version 4.0.0
# @since BUSCO 2.0.0
# 
# Copyright (c) 2016-2022, Evgeny Zdobnov (ez@ezlab.org)
# Licensed under the MIT license. See LICENSE.md file.

SIZE_RATIO <- 1
PLOT_SPECIES <- #PLOT_SPECIES#
PLOT_SPECIES <- factor(PLOT_SPECIES)
PLOT_SPECIES <- factor(PLOT_SPECIES,levels(PLOT_SPECIES)[c(length(levels(PLOT_SPECIES)):1)]) # reorder your species here just by changing the values in the vector :
PERCENTAGE_VALUES <- #PLOT_PERCENTAGE_VALUES#
ABSOLUTE_VALUES <- #PLOT_ABSOLUTE_VALUES#

labsize = 1
if (length(levels(PLOT_SPECIES)) > 10){
 labsize = 0.66
}

CATEGORY <- c(rep(c("S","D","F","M"),c(1)))
CATEGORY <-factor(CATEGORY)
CATEGORY = factor(CATEGORY,levels(CATEGORY)[c(4,1,2,3)])
DF = data.frame(PLOT_SPECIES, PERCENTAGE_VALUES, ABSOLUTE_VALUES, CATEGORY)

FIGURE <- ggplot() + 
  
  geom_bar(aes(y = PERCENTAGE_VALUES, x = PLOT_SPECIES, fill = CATEGORY), position = position_stack(reverse = TRUE), data = DF, stat = "identity", width = 0.75) + 
  coord_flip() + 
  theme_gray(base_size = 8) + 
  scale_y_continuous(labels = c("0","20","40","60","80","100"), breaks = c(0,20,40,60,80,100)) + 
  scale_fill_manual(
    values = c("#56B4E9", "#3492C7", "#F0E442", "#F04442"),
    labels = c(" Complete (C) and single-copy (S)  ",
              " Complete (C) and duplicated (D)",
              " Fragmented (F)  ",
              " Missing (M)")
  ) +   
  ggtitle("BUSCO Assessment Results") + 
  xlab("") + 
  ylab("\n%BUSCOs") + 

  theme(plot.title = element_text(family = "sans", hjust = 0.5, colour = "black", size = rel(2.2) * SIZE_RATIO, face = "bold")) + 
  theme(legend.position = "top", legend.title = element_blank()) + 
  theme(legend.text = element_text(family = "sans", size = rel(1.2) * SIZE_RATIO)) + 
  theme(panel.background = element_rect(color="#FFFFFF", fill = "white")) + 
  theme(panel.grid.minor = element_blank()) + 
  theme(panel.grid.major = element_blank()) +
  theme(axis.text.y = element_text(family = "sans", colour = "black", size = rel(1.66) * SIZE_RATIO)) + 
  theme(axis.text.x = element_text(family = "sans", colour = "black", size = rel(1.66) * SIZE_RATIO)) + 
  theme(axis.line = element_line(size = 1 * SIZE_RATIO, colour = "black")) + 
  theme(axis.ticks.length = unit(.85, "cm")) + 
  theme(axis.ticks.y = element_line(colour = "white", size = 0)) + 
  theme(axis.ticks.x = element_line(colour = "#222222")) + 
  theme(axis.ticks.length = unit(0.4, "cm")) + 
  theme(axis.title.x = element_text(family = "sans", size = rel(1.2) * SIZE_RATIO)) + 
  
  guides(fill = guide_legend(override.aes = list(colour = NULL))) +
  guides(fill = guide_legend(nrow = 2, byrow = TRUE))

for(i in rev(c(1:length(levels(PLOT_SPECIES))))){
  DETAILED_VALUES <- ABSOLUTE_VALUES[PLOT_SPECIES == PLOT_SPECIES[PLOT_SPECIES == levels(PLOT_SPECIES)[i]]]
  TOTAL_BUSCOS <- sum(DETAILED_VALUES)
  FIGURE <- FIGURE + 
  annotate("text", label = paste("C:", DETAILED_VALUES[1] + DETAILED_VALUES[2], " [S:", DETAILED_VALUES[1], ", D:", DETAILED_VALUES[2], "], F:", DETAILED_VALUES[3], ", M:", DETAILED_VALUES[4], ", n:", TOTAL_BUSCOS, sep = ""), 
          y = 3, x = i, size = labsize * 4 * SIZE_RATIO, colour = "black", hjust = 0, family = "sans")
}
FIGURE
```

```{r,echo=FALSE}
# Produce Table
if (nrow(BUSCO_INPUT) > 0){

DTABLE <- datatable(BUSCO_INPUT, 
  rownames = FALSE, 
  class = 'hover', 
  extensions  = 'Buttons', 
  filter = list(position = 'top'),
  options = list(
    search = list(regex = TRUE, caseInsensitive = FALSE),
    pageLength = 10,
    lengthMenu = c(5, 10, 15, 20),
    dom = '<"top"fB>rt<"bottom"lp>i<"clear">', 
    buttons = c('copy', 'csv', 'excel', 'pdf', 'colvis')
  )
)
DTABLE 
}
```

#### Links and Citation
If you publish the results use following citation:

*Mosè Manni, Matthew R Berkeley, Mathieu Seppey, Felipe A Simão, Evgeny M Zdobnov,*
*BUSCO Update: Novel and Streamlined Workflows along with Broader and Deeper Phylogenetic Coverage for Scoring of Eukaryotic, Prokaryotic, and Viral Genomes.*
*Molecular Biology and Evolution, Volume 38, Issue 10, October 2021, Pages 4647–4654*